---
title       : COVID-19 in South East Asia
subtitle    : Group Project - R Web Apps Using Shiny (WQD7001)
author      : Group 4
job         : Muhammad Ezlan Zakhir Khan (S2116731), Muhammad Amirul Daniel Badrul Hisham (S2115750), Kristian Surya Dinata (S2043845), Shu Meei Law (S2117388), Eva Ying Ying Chin (S2115794)
framework   : io2012  # {io2012, html5slides, shower, dzslides, ...}
highlighter : highlight.js  # {highlight.js, prettify, highlight}
hitheme     : tomorrow      # 
widgets     : [shiny, interactive]  # {mathjax, quiz, bootstrap}
ext_widgets : {rCharts: [libraries/nvd3]}
mode        : selfcontained # {standalone, draft}
knit        : slidify::knit2slides
---

## Introduction - The Development of Data Product

Application : Covid-19 trend to the economic impact in ASEAN Countries (2019 - 2021)
The repository consists of three final files:
- ui.R
- server.R
- README.md

Data file:
- covid_data.csv
- Economic_data.csv
- VaccineData.csv

For more details, please visit:
- Shiny Apps: 
- GitHub: https://github.com/Kristian2828/PDS-Assignment

--- .class #id 

## R Shiny Apps - ui.R
Below shown part of the coding extracted from ui.R:
```{r}
ui <- fluidPage(
    tabPanel("Cases", value = "Cases",
             sidebarLayout(
               sidebarPanel(
                 h1("COVID-19 in South East Asia"),
                 selectInput(inputId = "dv", label = "Category",
                             choices = c("Total_Cases","New_Cases", "Total_Death","New_Death"),
                             selected = "New_Cases"),
                 selectInput(inputId = "Country", "Country(s)",
                             choices = levels(covid$Country),
                             multiple = TRUE,
                             selected = c("Malaysia")),
                 dateRangeInput(inputId = "date", "Date range",
                                start = min(covid$Date),
                                end   = max(covid$Date)),
                 downloadButton(outputId = "download_data", label = "Download"),
               ),
               mainPanel(
                 plotlyOutput(outputId = "plot"), br(),
                 strong(em("COVID-19 CASES IN SOUTH EAST ASIA")),
                 br(), br(), br(),
                 DT::dataTableOutput(outputId = "table")
               )
             )),)
```

--- .class #id 
## R Shiny Apps - server.R
Below shown part of the coding extracted from server.R:
```{r}
server <- function(input, output) {
  filtered_data <- reactive({
    subset(covid,
           Country %in% input$Country &
             Date >= input$date[1] & Date <= input$date[2])})
  
  output$plot <- renderPlotly({
    ggplotly({
      p <- ggplot(filtered_data(), aes_string(x="Date", y=input$dv, color="Country")) +
        geom_point(alpha=0.5) + theme(legend.position = "none") +
        ylab("Total Number")
      p
    })
  })
  }
```

--- .class #id
## R Shiny Visualization
Below shown one example of the R Shiny visualization in our data product:
```{r echo = F, results = 'asis'}
require(rCharts)
## Read files
covid = read.csv("C:/Users/evach/OneDrive/Documents/covid_data.csv", sep = ';')

## Change/update the variable structure
covid$Date = as.Date(covid$Date)
covid$Country = as.factor(covid$Country)


n1 <- nPlot(New_Cases ~ Date, group = 'Country', type = 'scatterPlusLineChart',
  data = covid)
n1$print('chart1')
```
---
```{r, echo=FALSE}
library(shiny)
library(plotly)
library(DT)
library(shinythemes)
library(ggcorrplot)
library(correlation)

## Read files
covid = read.csv("C:/Users/evach/OneDrive/Documents/covid_data.csv", sep = ';')
eco_data <- read.csv("C:/Users/evach/OneDrive/Documents/Economic_Data.csv")
covid$Date = as.Date(covid$Date)
covid$Country = as.factor(covid$Country)
vaccinedata <- read.csv("C:/Users/evach/OneDrive/Documents/VaccineData.csv", header = TRUE, sep = ",")
vaccinedata$Date <- strptime(as.character(vaccinedata$Date),format="%d/%m/%Y")
vaccinedata$Date <- as.POSIXct(vaccinedata$Date)
vaccinedata$Date <- as.Date(vaccinedata$Date)
vaccinedata$Entity <- as.factor(vaccinedata$Entity)


## Change/update the variable structure
covid$Date = as.Date(covid$Date)
covid$Country = as.factor(covid$Country)
eco_data$Country = as.factor(eco_data$Country)
eco_data$Date = as.Date(eco_data$Date)
```

```{r opts.label = 'shiny'}
slidifyUI(
  sidebarPanel(
    h1("COVID-19 in South East Asia"),
    selectInput(inputId = "dv", label = "Category",
                choices = c("Total_Cases","New_Cases", "Total_Death","New_Death"),
                selected = "New_Cases"),
    selectInput(inputId = "Country", "Country(s)",
                choices = levels(covid$Country),
                multiple = TRUE,
                selected = c("Malaysia")),
    dateRangeInput(inputId = "date", "Date range",
                   start = min(covid$Date),
                   end   = max(covid$Date)),
    downloadButton(outputId = "download_data", label = "Download"),
  ),
  mainPanel(
    plotlyOutput(outputId = "plot"), br(),
    strong(em("COVID-19 CASES IN SOUTH EAST ASIA")),
    br(), br(), br(),
    DT::dataTableOutput(outputId = "table")
  )
)
```
---
